---
title: "ANOVA Model for NBA Salary"
author: "Mukund Vegunta"
date: "2026-05-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readr)
dataset <- read_csv("C:/Users/mukun/OneDrive - University of Illinois - Urbana/NBA Datasets/cleaned_dataset.csv")
```

#ANOVA to See if There is a Statistically Signifcant Difference in Salary Among Positions
```{r}
y <- dataset[["salary_2025_26"]]
x <- factor(dataset[["Pos_pg"]])
anova_model <- aov(y ~ x, data = dataset)
summary(anova_model)

```
```{r}
model.tables(anova_model, type = "means")
```
At a 5% signficance level, there is not enough evidence to prove that there is a difference between player salaries depending on the position they play. However, a p-value of 0.0581 is still very low and with a higher signifiance level, there is evidence to suggest a potential difference in NBA player salary by position. Typically, point guards have the highest salary of 15409581, while shooting guards have the lowest salary of 9943616. 



